### 2023-09-07 3.Design/crossbar.tex
Added crossbar part, may be removed

This section is here to show

>>>>

The crossbar circuit has already been explained in the section \ref{sec:crossbar},

    Since the analog system is only simulated in the inference phase of the \ac{NN}, the resistance doesn't need to change during this phase. The weights only change during the training phase, and the resistances are just a rendition of the weights (section TODO : ref weigths to res)
